---
title: "F627-F630 comparison"
author: "Jon Ahlinder"
date: "2023-02-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/Users/joah/OneDrive - Skogforsk/Documents/Projekt/Treeplan/BetulaS23/F627-F630/")
require(dplyr)
require(ggplot2)
library(asreml)
require(asremlPlus)
library(rcompanion) # For normal score transformation
library(lmerTest)
library(tidyverse)
library(ggpubr)
library(knitr)
```

## Read data
Data from dataplan
```{r}
DMS_F627 <- read.csv(file = "DMS_stems_F627.txt",header = T,sep = ",")
DMS_F628 <- read.csv(file = "DMS_stems_F628.txt",header = T,sep = ",")
DMS_F629 <- read.csv(file = "DMS_stems_F629.txt",header = T,sep = ",")
DMS_F630 <- read.csv(file = "DMS_stems_F630.txt",header = T,sep = ",")
# Add family origin
DMS_F627$Origin <- ifelse(grepl("F01FP",DMS_F627$Mum_name),'Finland','Sweden')
DMS_F628$Origin <- ifelse(grepl("F01FP",DMS_F628$Mum_name),'Finland','Sweden')
DMS_F629$Origin <- ifelse(grepl("F01FP",DMS_F629$Mum_name),'Finland','Sweden')
DMS_F630$Origin <- ifelse(grepl("F01FP",DMS_F630$Mum_name),'Finland','Sweden')
DMS_F627 %>% group_by(Origin) %>% summarize(
                                      count = n(),
                                       mean = mean(Hjd_20, na.rm = TRUE), 
                                         sd = sd(Hjd_20, na.rm = TRUE)) 
# Remove uninformative columns
DMS_F627 <- DMS_F627 %>%
  select(-c(East,North,Grid,Colb,Rowb,contains("_n"),contains("Surface_sum"),contains("Design_sum"),contains("Local_trend"),contains("Bv_exclude"),contains("Skad"))) %>%
  mutate(Trial = "F627")
DMS_F628 <- DMS_F628 %>%
  select(-c(East,North,Grid,Colb,Rowb,contains("_n"),contains("Surface_sum"),contains("Design_sum"),contains("Local_trend"),contains("Bv_exclude"),contains("Skad"))) %>%
  mutate(Trial = "F628")
DMS_F629 <- DMS_F629 %>%
  select(-c(East,North,Grid,Colb,Rowb,contains("_n"),contains("Surface_sum"),contains("Design_sum"),contains("Local_trend"),contains("Bv_exclude"),contains("Skad"))) %>%
  mutate(Trial = "F629")
DMS_F630 <- DMS_F630 %>%
  select(-c(East,North,Grid,Colb,Rowb,contains("_n"),contains("Surface_sum"),contains("Design_sum"),contains("Local_trend"),contains("Bv_exclude"),contains("Skad"))) %>%
  mutate(Trial = "F630")
```

## Merge data

```{r}
common_cols1 <- intersect(colnames(DMS_F627), colnames(DMS_F628))
common_cols2 <- intersect(common_cols1, colnames(DMS_F629))
common_cols <- intersect(common_cols2, colnames(DMS_F630))
print(common_cols)
DMS_F627_c <- DMS_F627 %>% 
  select(all_of(common_cols))
DMS_F628_c <- DMS_F628 %>% 
  select(all_of(common_cols))
DMS_F629_c <- DMS_F629 %>% 
  select(all_of(common_cols))
DMS_F630_c <- DMS_F630 %>% 
  select(all_of(common_cols))
DMS_trials <- rbind(DMS_F627_c,DMS_F628_c,DMS_F629_c,DMS_F630_c)
rm(DMS_F627_c,DMS_F628_c,DMS_F629_c,DMS_F630_c)
DMS_trials$Sortnr <- as.factor(DMS_trials$Sortnr)
DMS_F627 %>% group_by(Origin) %>% summarize(
                                      count = n(),
                                       mean = mean(Hjd_20, na.rm = TRUE), 
                                         sd = sd(Hjd_20, na.rm = TRUE))
DMS_F628 %>% group_by(Origin) %>% summarize(
                                      count = n(),
                                       mean = mean(Hjd_20, na.rm = TRUE), 
                                         sd = sd(Hjd_20, na.rm = TRUE))
DMS_F629 %>% group_by(Origin) %>% summarize(
                                      count = n(),
                                       mean = mean(Hjd_20, na.rm = TRUE), 
                                         sd = sd(Hjd_20, na.rm = TRUE))
DMS_F630 %>% group_by(Origin) %>% summarize(
                                      count = n(),
                                       mean = mean(Hjd_20, na.rm = TRUE), 
                                         sd = sd(Hjd_20, na.rm = TRUE))

```


## Plot phenotypic records

```{r}
DMS_trials <- DMS_trials %>% 
  select(-c(Stem_id,Genotype_id,Mum_id,Mum_type,Dad_id,Dad_type,Family_id,Ploc))
write.table(x = DMS_trials, file = "Data_F627_628_629_630.txt",sep="\t",quote = FALSE,row.names = FALSE) 
p3 <- DMS_trials %>% group_by(Origin,Sortnr,Trial) %>% summarize(
                                      count = n(),
                                       Mean = mean(Hjd_20, na.rm = TRUE), 
                                         Sd = sd(Hjd_20, na.rm = TRUE)) %>%
  ggplot(aes(x = Sortnr,y = Mean,fill = Origin)) + 
  geom_bar(stat="identity", color="black") + 
  scale_fill_manual(values=c("#56B4E9","#E69F00")) + 
  facet_wrap(~Trial,scales = "free") +
  theme(axis.text.x = element_blank()) +
  geom_errorbar(aes(ymin=Mean-Sd, max=Mean+Sd), width=.2, position=position_dodge(width=0.7)); p3
p4 <- DMS_trials %>% group_by(Origin,Sortnr,Trial) %>% summarize(
                                      count = n(),
                                       Mean = mean(Dia_20, na.rm = TRUE), 
                                         Sd = sd(Dia_20, na.rm = TRUE)) %>%
  ggplot(aes(x = Sortnr,y = Mean,fill = Origin)) + 
  geom_bar(stat="identity", color="black") + 
  scale_fill_manual(values=c("#56B4E9","#E69F00")) + 
  facet_wrap(~Trial,scales = "free") +
  theme(axis.text.x = element_blank()) +
  geom_errorbar(aes(ymin=Mean-Sd, max=Mean+Sd), width=.2, position=position_dodge(width=0.7)); p4  


```

## Transform traits
Calculate volume, production, and normal score transform Gkva and Klyk. Check Vitality too! Some traits should perhaps be log-transformed.
```{r}
# Transform height and diameter to meter unit
DMS_trials <- DMS_trials %>% 
  mutate(Hjd_20 = Hjd_20*0.1) %>% # dm to m
  mutate(Dia_20 = Dia_20*0.1) # mm to cm
# per hectare volume production (5 x 5 parcel of size 10 x 10 meter which is 100 square meters), volume functions gives volume in cubic dm which is a factor 100 less if converted to cubic meters
DMS_trials2 <- DMS_trials %>%  mutate(Vol_20_1 = (10^-0.84627 * Dia_20^2.23818 * (Dia_20 + 20)^-1.06930 * Hjd_20^6.02015 * (Hjd_20 - 1.3)^-4.51472)) %>% 
  mutate(Vol_20_2 = exp(2.10253*log(Dia_20+0.0001) + 3.98519*log(Hjd_20+0.00001) - 2.65900*log(Hjd_20 - 1.3) - 0.0140970*Dia_20 - 4.49213)) %>% 
  mutate(Vol_20 = Vol_20_1) %>%  
  mutate(GkvaNScore_20 = blom(Gkva_20)) %>% # 20 year measurement
  mutate(KlykNScore_20 = blom(Klyk_20)) %>% # 20 year measurement
  mutate(GkvaNScore_10 = blom(Gkva_10)) %>% # 10 year measurement
  mutate(KlykNScore_10 = blom(Klyk_10)) %>% # 10 year measurement
  mutate(VitNScore_20 = blom(Vit_20)) # 20 year measurement
# Brandel, G. 1990. Volymfunktioner för enskilda träd. Tall, gran och björk. SLU, Inst f skogsproduktion, Rapport 26, 72 s., Garpenberg. Sammanfattning i Fakta Skog nr 11, 1994.
  cor.test(DMS_trials2$Vol_20_1,DMS_trials2$Vol_20_2) # both measures almost identical
p1 <- ggplot(data = DMS_trials2, aes(x = GkvaNScore_20)) + 
  geom_histogram(color="black", fill="green") +
  ggtitle(label = "Normal score transformed branch quality at age 20"); p1
p2 <- ggplot(data = DMS_trials2, aes(x = GkvaNScore_10)) + 
  geom_histogram(color="black", fill="green") +
  ggtitle(label = "Normal score transformed branch quality at age 10"); p2
p3 <- ggplot(data = DMS_trials2, aes(x = KlykNScore_20)) + 
  geom_histogram(color="black", fill="yellow") +
  ggtitle(label = "Normal score transformed forking at age 20"); p3
p4 <- ggplot(data = DMS_trials2, aes(x = KlykNScore_10)) + 
  geom_histogram(color="black", fill="yellow") +
  ggtitle(label = "Normal score transformed forking at age 10"); p4
p5 <- ggplot(data = DMS_trials2, aes(x = VitNScore_20)) + 
  geom_histogram(color="black", fill="blue") +
  ggtitle(label = "Normal score transformed Vitality at age 20"); p5
p6 <- ggplot(data = DMS_trials2, aes(x = Vol_20)) + 
  geom_histogram(color="black", fill="red") +
  ggtitle(label = "Volume production per hectare at age 20"); p6
p7 <- ggplot(data = DMS_trials2, aes(x = log(Vol_20))) + 
  geom_histogram(color="black", fill="red") +
  ggtitle(label = "Logarithm of volume production per hectare at age 20"); p7


```

## LMM analysis single trial

```{r}
############## us i.e. unstructured residual ##############
#DMS_F627 <- DMS_trials %>% 
#  filter(Trial == "F627") %>%
#  mutate(across(c(Trial,Sortnr,Ruta,Rad,Planta),factor))
# First single trait
# Volume at year 20
#lp.asr.u <- asreml(
#  fixed = Vol_20 ~ 1,
#  random = ~ idv(Sortnr) + idv(Ruta) + idv(Ruta):Rad + idv(Ruta):Planta,
#  data = DMS_F627,
#  residual = ~id(units),
#  ai.sing=TRUE,
#  maxit = 200
#)
# Multiple trait
#lp.asr.u <- asreml(
#  fixed = cbind(Vol_20,GkvaNScore_10,KlykNScore_20,VitNScore_20) ~ trait,
#  random = ~ us(trait):Sortnr + us(trait):Ruta + us(trait):Ruta:Rad + us(trait):Ruta:Planta,
#  residual = ~ id(units):us(trait),
#  data = DMS_F627,
#  na.action = na.method(x = "include", y = "include"),
#  start.values = FALSE,
#  maxit = 200
#)
```

## LMM analysis multiple trials
Using ASReml-R, multiple-trial analysis, multi-trait. As predictors, I include the fixed effect of environment i, the random effect of family (i.e. sortnr) j, the random interaction between genotype j and environment i,
and the random effect of block k nested in environment i 
```{r}
# First add an interaction term between Sortnr and trial
#DMS_trials %>%
#  mutate(GxE = Sortnr * Trial)
DMS_trials2 <- DMS_trials2 %>%
mutate(across(c(Trial,Sortnr,Ruta,Rad,Planta),factor))
############## us i.e. unstructured residual ##############
# Fit the model
model <- asreml(fixed = cbind(Vol_20,GkvaNScore_10,KlykNScore_20,VitNScore_20) ~ trait + at(trait):Trial,
          random = ~ us(trait):Sortnr: + us(trait):Sortnr:Trial + us(trait):Trial:Ruta,
          residual = ~ id(units):us(trait),
          na.action = na.method(x = "include", y = "include"),
          data = DMS_trials2,
          maxit = 1000)
test <- wald.asreml(model, denDF = "default", ssType = "conditional")$Wald; test
summary(model, coef = TRUE)$coef.fi
summary(model)$varcomp

vpredict(model, r_A ~ V8 / sqrt(V7 * V9))
#lp.asr.u <- asreml(
#  fixed = cbind(Vol_20,GkvaNScore_10,KlykNScore_20,VitNScore_20) ~ trait + Trial,
#  random = ~ us(trait, init = rep(0,6)):Sortnr +
#    us(trait, init = rep(0,6)):at(Sortnr):us(trait, init = rep(0,6)):at(Trial),
#  residual = ~ id(units):us(trait), # , init = rep(0,6)
#  data = DMS_trials,
#  na.action = na.method(x = "include", y = "include"),
#  start.values = TRUE,
#  maxit = 200
#)
```

## Fixed effect ANOVA analysis
Volume at year 20
```{r}
# Remove Fältnr not present in three out of four trials
DMS_subset <- DMS_trials2 %>% 
  filter(Sortnr == 1 | Sortnr == 2 | Sortnr == 5 | Sortnr == 8 | Sortnr == 9 | Sortnr == 12) %>% # Sortnr 13 removed  | Sortnr == 13
  mutate(across(c(Trial,Sortnr,Ruta,Rad,Planta),factor))
# Recode Fältnr according to origin
DMS_subset$Sortnr <- recode_factor(DMS_subset$Sortnr, "1" = "Pltg Sv373","2" = "Pltg Sv379", "5" = "Pltg Sv390","8" = "Frötäkt1089", "9" = "F250Sävar", "12" = "Plus 62-64") # , "13" = "Plus 64-66"
## Plot of per hectare volume production per sortnr
p8 <- DMS_subset %>% group_by(Origin,Sortnr,Trial) %>% summarize(
                                      count = n(),
                                       Mean = mean(Vol_20, na.rm = TRUE), 
                                         Sd = sd(Vol_20, na.rm = TRUE)) %>%
  ggplot(aes(x = Sortnr,y = Mean,fill = Origin)) + 
  geom_bar(stat="identity", color="black") + 
  scale_fill_manual(values=c("#56B4E9","#E69F00")) + 
  facet_wrap(~Trial,scales = "free") +
  theme(axis.text.x = element_text(angle = 90,size = 6),axis.title.x = element_blank()) +
  ylab("Volume production per hectare") +
  geom_errorbar(aes(ymin=Mean-Sd, max=Mean+Sd), width=.2, position=position_dodge(width=0.7)); p8 
ggsave(filename = "Figures/barplot_across_trial_volume_production.png",plot = p8,dpi = "print")
p6 <- ggboxplot(DMS_subset, x = "Sortnr", y = "Vol_20") +
  facet_wrap(~Trial,scales = "free") +
  theme(axis.title.x = element_blank(),axis.text.x = element_text(angle = 90,size = 6), axis.text.y = element_text(size = 8)); p6 # Visualize Sortnr differences in Volume at year 20
p7 <- ggboxplot(
  DMS_subset, x = "Sortnr", y = "Vol_20",
  color = "Trial", palette = "jco"
  ); p7

# Linear model with only fixed effects
lm1 <- lm(Vol_20 ~ Trial + Sortnr + Trial:Sortnr + Trial:Ruta, data = DMS_subset)
summary(lm1) # Too many classes
hist(resid(lm1),nclass = 30) # should be normally distributed
#create Q-Q plot for residuals
qqnorm(resid(lm1))

#add a straight diagonal line to the plot
qqline(resid(lm1)) 
# ANOVA
an2 <- aov(lm1)
summary(an2)

# Save the output to a text file
output <- capture.output(summary(an2))
writeLines(output, "output_anova_production_20.txt")
write.table(output, "output_anova_production_20.txt", sep = "\t",quote=FALSE,row.names = FALSE)
par(mfrow=c(2,2))
plot(an2)
par(mfrow=c(1,1))
tukey.two.way<-TukeyHSD(an2) # To find out which groups are statistically different from one another, you can perform a Tukey’s Honestly Significant Difference (Tukey’s HSD) post-hoc test for pairwise comparisons
#plot(tukey.two.way, las = 2)

# plot trial effect comparison
CIlow <-tukey.two.way$Trial[,'lwr']
CIhigh <- tukey.two.way$Trial[,'upr']
  pt <- tukey.two.way$Trial %>%
    as.data.frame(.) %>%
    rownames_to_column(.)  %>%
    rename(Estimate = diff,Comparison = rowname) %>%
  ggplot(aes(x=Comparison,y=Estimate)) +  
  geom_point(size = 0.1) +
  geom_pointrange(aes(ymin = CIlow,ymax = CIhigh)) +
  coord_flip() +
  theme_bw() +
  xlab("Comparison") +
  ylab("Estimate") +
  geom_hline(yintercept=0,lty = 2) + 
  scale_y_continuous(expand = c(0,0)); pt
# Plot Sortnr comparison
CIlow <-tukey.two.way$Sortnr[,'lwr']
CIhigh <- tukey.two.way$Sortnr[,'upr']
  ps <- tukey.two.way$Sortnr %>%
    as.data.frame(.) %>%
    rownames_to_column(.)  %>%
    rename(Estimate = diff,Comparison = rowname) %>%
  ggplot(aes(x=Comparison,y=Estimate)) +  
  geom_point(size = 0.1) +
  geom_pointrange(aes(ymin = CIlow,ymax = CIhigh)) +
  coord_flip() +
  theme_bw() +
  xlab("Comparison") +
  ylab("Estimate") +
  geom_hline(yintercept=0,lty = 2) + 
  scale_y_continuous(expand = c(0,0)); ps
```

Vitality at year 20 (normal score transformed)

```{r}
p8 <- ggboxplot(DMS_subset, x = "Sortnr", y = "VitNScore_20") +
  facet_wrap(~Trial,scales = "free") +
  theme(axis.title.x = element_blank(),axis.text.x = element_text(angle = 90,size = 6), axis.text.y = element_text(size = 8)); p8 # Visualize Sortnr differences in Volume at year 20
p9 <- ggboxplot(
  DMS_subset, x = "Sortnr", y = "VitNScore_20",
  color = "Trial", palette = "jco"
  ); p9

# Linear model with only fixed effects
lm1 <- lm(VitNScore_20 ~ Trial + Sortnr + Trial * Sortnr + Ruta * Trial + Rad * Trial + Planta * Trial, data = DMS_subset)
#summary(lm1) # Too many classes 
hist(resid(lm1),nclass = 30) # should be normally distributed
#create Q-Q plot for residuals
qqnorm(resid(lm1))

#add a straight diagonal line to the plot
qqline(resid(lm1)) 
# ANOVA
an2 <- aov(lm1)
par(mfrow=c(2,2))
plot(an2)
par(mfrow=c(1,1))
tukey.two.way<-TukeyHSD(an2) # To find out which groups are statistically different from one another, you can perform a Tukey’s Honestly Significant Difference (Tukey’s HSD) post-hoc test for pairwise comparisons
#plot(tukey.two.way, las = 2)

# plot trial effect comparison
CIlow <-tukey.two.way$Trial[,'lwr']
CIhigh <- tukey.two.way$Trial[,'upr']
  pt2 <- tukey.two.way$Trial %>%
    as.data.frame(.) %>%
    rownames_to_column(.)  %>%
    rename(Estimate = diff,Comparison = rowname) %>%
  ggplot(aes(x=Comparison,y=Estimate)) +  
  geom_point(size = 0.1) +
  geom_pointrange(aes(ymin = CIlow,ymax = CIhigh)) +
  coord_flip() +
  theme_bw() +
  xlab("Comparison") +
  ylab("Estimate") +
  geom_hline(yintercept=0,lty = 2) + 
  scale_y_continuous(expand = c(0,0)); pt2
# Plot Sortnr comparison
CIlow <-tukey.two.way$Sortnr[,'lwr']
CIhigh <- tukey.two.way$Sortnr[,'upr']
  ps2 <- tukey.two.way$Sortnr %>%
    as.data.frame(.) %>%
    rownames_to_column(.)  %>%
    rename(Estimate = diff,Comparison = rowname) %>%
  ggplot(aes(x=Comparison,y=Estimate)) +  
  geom_point(size = 0.1) +
  geom_pointrange(aes(ymin = CIlow,ymax = CIhigh)) +
  coord_flip() +
  theme_bw() +
  xlab("Comparison") +
  ylab("Estimate") +
  geom_hline(yintercept=0,lty = 2) + 
  scale_y_continuous(expand = c(0,0)); ps2
```

Analyzing trait branch quality at age 10

```{r}
p10 <- ggboxplot(DMS_subset, x = "Sortnr", y = "GkvaNScore_10") +
  facet_wrap(~Trial,scales = "free") +
  theme(axis.title.x = element_blank(),axis.text.x = element_text(angle = 90,size = 6), axis.text.y = element_text(size = 8)); p10 # Visualize Sortnr differences in Volume at year 20
p11 <- ggboxplot(
  DMS_subset, x = "Sortnr", y = "GkvaNScore_10",
  color = "Trial", palette = "jco"
  ); p11

# Linear model with only fixed effects
lm1 <- lm(GkvaNScore_10 ~ Trial + Sortnr + Trial * Sortnr + Ruta * Trial + Rad * Trial + Planta * Trial, data = DMS_subset)
#summary(lm1) # Too many classes 
hist(resid(lm1),nclass = 30) # should be normally distributed
#create Q-Q plot for residuals
qqnorm(resid(lm1))

#add a straight diagonal line to the plot
qqline(resid(lm1)) 
# ANOVA
an2 <- aov(lm1)
par(mfrow=c(2,2))
plot(an2)
par(mfrow=c(1,1))
tukey.two.way<-TukeyHSD(an2) # To find out which groups are statistically different from one another, you can perform a Tukey’s Honestly Significant Difference (Tukey’s HSD) post-hoc test for pairwise comparisons
#plot(tukey.two.way, las = 2)

# plot trial effect comparison
CIlow <-tukey.two.way$Trial[,'lwr']
CIhigh <- tukey.two.way$Trial[,'upr']
  pt3 <- tukey.two.way$Trial %>%
    as.data.frame(.) %>%
    rownames_to_column(.)  %>%
    rename(Estimate = diff,Comparison = rowname) %>%
  ggplot(aes(x=Comparison,y=Estimate)) +  
  geom_point(size = 0.1) +
  geom_pointrange(aes(ymin = CIlow,ymax = CIhigh)) +
  coord_flip() +
  theme_bw() +
  xlab("Comparison") +
  ylab("Estimate") +
  geom_hline(yintercept=0,lty = 2) + 
  scale_y_continuous(expand = c(0,0)); pt3
# Plot Sortnr comparison
CIlow <-tukey.two.way$Sortnr[,'lwr']
CIhigh <- tukey.two.way$Sortnr[,'upr']
  ps3 <- tukey.two.way$Sortnr %>%
    as.data.frame(.) %>%
    rownames_to_column(.)  %>%
    rename(Estimate = diff,Comparison = rowname) %>%
  ggplot(aes(x=Comparison,y=Estimate)) +  
  geom_point(size = 0.1) +
  geom_pointrange(aes(ymin = CIlow,ymax = CIhigh)) +
  coord_flip() +
  theme_bw() +
  xlab("Comparison") +
  ylab("Estimate") +
  geom_hline(yintercept=0,lty = 2) + 
  scale_y_continuous(expand = c(0,0)); ps3
```

Analyzing trait Forking at age 20

```{r}
p12 <- ggboxplot(DMS_subset, x = "Sortnr", y = "KlykNScore_20") +
  facet_wrap(~Trial,scales = "free") +
  theme(axis.title.x = element_blank(),axis.text.x = element_text(angle = 90,size = 6), axis.text.y = element_text(size = 8)); p12 # Visualize Sortnr differences in Volume at year 20
p13 <- ggboxplot(
  DMS_subset, x = "Sortnr", y = "KlykNScore_20",
  color = "Trial", palette = "jco"
  ); p13

# Linear model with only fixed effects
lm1 <- lm(KlykNScore_20 ~ Trial + Sortnr + Trial * Sortnr + Ruta * Trial + Rad * Trial + Planta * Trial, data = DMS_subset)
#summary(lm1) # Too many classes 
hist(resid(lm1),nclass = 30) # should be normally distributed
#create Q-Q plot for residuals
qqnorm(resid(lm1))

#add a straight diagonal line to the plot
qqline(resid(lm1)) 
# ANOVA
an2 <- aov(lm1)
par(mfrow=c(2,2))
plot(an2)
par(mfrow=c(1,1))
tukey.two.way<-TukeyHSD(an2) # To find out which groups are statistically different from one another, you can perform a Tukey’s Honestly Significant Difference (Tukey’s HSD) post-hoc test for pairwise comparisons
#plot(tukey.two.way, las = 2)

# plot trial effect comparison
CIlow <-tukey.two.way$Trial[,'lwr']
CIhigh <- tukey.two.way$Trial[,'upr']
  pt4 <- tukey.two.way$Trial %>%
    as.data.frame(.) %>%
    rownames_to_column(.)  %>%
    rename(Estimate = diff,Comparison = rowname) %>%
  ggplot(aes(x=Comparison,y=Estimate)) +  
  geom_point(size = 0.1) +
  geom_pointrange(aes(ymin = CIlow,ymax = CIhigh)) +
  coord_flip() +
  theme_bw() +
  xlab("Comparison") +
  ylab("Estimate") +
  geom_hline(yintercept=0,lty = 2) + 
  scale_y_continuous(expand = c(0,0)); pt4
# Plot Sortnr comparison
CIlow <-tukey.two.way$Sortnr[,'lwr']
CIhigh <- tukey.two.way$Sortnr[,'upr']
  ps4 <- tukey.two.way$Sortnr %>%
    as.data.frame(.) %>%
    rownames_to_column(.)  %>%
    rename(Estimate = diff,Comparison = rowname) %>%
  ggplot(aes(x=Comparison,y=Estimate)) +  
  geom_point(size = 0.1) +
  geom_pointrange(aes(ymin = CIlow,ymax = CIhigh)) +
  coord_flip() +
  theme_bw() +
  xlab("Comparison") +
  ylab("Estimate") +
  geom_hline(yintercept=0,lty = 2) + 
  scale_y_continuous(expand = c(0,0)); ps4
```



